Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Edit ASSR section

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. While this can be addressed in the supervised case using late integration of discriminative classifiers (see Section \ref{sec:eili}), this is not direclty feasible in the unsupervised case. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest.

@@

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,q}^u \Vert \Vert \mu_n^v - \mu_{n,q}^v \Vert} \right).
\end{equation} 
Here, $\mu_{m,q}^u$ and $\mu_{n,q}^v$ are the $q^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item Relevance-based Quantization closest similarity (\emph{RbQ-c}): the similarity between two scenes $s_u$ and $s_v$ is equal to the largest similarity between their centroids, that is
\begin{equation}
	\max_{m,n} K_{mn}^{uv},
\end{equation}
\item Relevance-based Quantization average similarity  (\emph{RbQ-a}): the similarity between two scenes $s_u$ and $s_v$ is equal to the average of their centroid similarities, that is
\begin{equation}
	\frac{1}{M^2} \sum_{m,n} K_{mn}^{uv}
\end{equation}
and,
\item Relevance-based Quantization weighted similarity  (\emph{RbQ-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids weighted by the number of frames assigned to its cluster.
\end{itemize}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D_{mn}^{uv}=1-K_{mn}^{uv}.
\end{equation*}
As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

>>>>

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. While this can be addressed in the supervised case using late integration of discriminative classifiers (see Section \ref{sec:eili}), this is not directly feasible in the unsupervised case. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest.

@@

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with a local scaling method \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,q}^u \Vert \Vert \mu_n^v - \mu_{n,q}^v \Vert} \right).
\end{equation} 
Here, $\mu_{m,q}^u$ and $\mu_{n,q}^v$ are the $q^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item Relevance-based Quantization closest similarity (\emph{RbQ-c}): the similarity between two scenes $s_u$ and $s_v$ is equal to the largest similarity between their centroids, that is
\begin{equation}
	\max_{m,n} K_{mn}^{uv},
\end{equation}
\item Relevance-based Quantization average similarity  (\emph{RbQ-a}): the similarity between two scenes $s_u$ and $s_v$ is equal to the average of their centroid similarities, that is
\begin{equation}
	\frac{1}{M^2} \sum_{m,n} K_{mn}^{uv}
\end{equation}
and,
\item Relevance-based Quantization weighted similarity  (\emph{RbQ-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids each weighted by the number of frames assigned to its cluster.
\end{itemize}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$ which is computed from $K$:
\begin{equation*}
D_{mn}^{uv}=1-K_{mn}^{uv}.
\end{equation*}
